### 2015-05-24 docs/report/overview.tex
Fix array partition section and bib links

\section{Library Overview}\label{sec:overview}
JavaScript developers are familiar with the concept of map, filter and reduce skeletons as language constructs. In JavaScript, \code{Array}s have \code{map}, \code{filter}, and \code{reduce} functions and version 6 of the EcmaScript standard adds those same methods to \ttarray{}s \cite{es6-ta}. For example, to multiply all the elements of an \code{Array} by two:
\begin{lstlisting}[caption=Example creating a new array with the values of the original one multiplied by two]
var newValues = [1,2,3,4].map(function(e){
  return e * 2;
});

>>>>

\section{Library Overview}\label{sec:overview}
JavaScript developers are familiar with the concept of map, filter and reduce skeletons as language constructs. In JavaScript, \code{Array}s have \code{map}, \code{filter}, and \code{reduce} functions and version 6 of the EcmaScript standard adds those same methods to \ttarray{}s \cite{es6}. For example, to multiply all the elements of an \code{Array} by two:
\begin{lstlisting}[caption=Example creating a new array with the values of the original one multiplied by two]
var newValues = [1,2,3,4].map(function(e){
  return e * 2;
});
